Supplementary Information

### 2015-09-04 manuscript/supplement.tex
updated refs to supplemental figures

    Unlike species richness, only generality showed an overall increase with
    increasing proportions of basal resources in a web ($\beta_0$=0.019,
    $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
    link density, generality, and vulnerability, respectively;
    Fig.~\ref{props_v_lat}). In each case, however, there were substantial
    effects of latitude on the scaling relationships. Thus, the scaling
    exponents for link density and vulnerability were negative for estuarine,
    lake, and stream communities and became more negative towards the poles
    ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
    $p$\textless0.001, respectively; Fig.~\ref{BIT}). For the scaling of link
    density and vulnerability in marine and terrestrial communities, the overall
    effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
    $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
    $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
    $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
    that there was weak scaling at most latitudes. In contrast, the scaling
    exponent of generality with the proportion of basal resources was positive
    near the equator and negative near the poles in estuarine, lake, and stream
    communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
    very little change in the scaling exponents for marine and terrestrial
    communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
    $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).

    As with species richness, link density, generality, and vulnerability
    generally increased with the proportion of intermediate consumers in a web
    ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
    $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). 
    The best-fit models for link density and vulnerability did not include
    any effect of latitude. In contrast, the strength of the scaling relationship
    for generality increased weakly towards the poles in estuarine, marine, and
    terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
    towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
    and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{BIT}).

    In contrast to the generally positive scaling relationships above, link
    density, generality, and vulnerability decreased as the proportion of top
    predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
    $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
    Fig~\ref{props_v_lat}). For estuarine, lake, and marine food webs the
    strength of this scaling did not vary significantly with latitude
    ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
    $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
    In stream and terrestrial food webs, however, scaling was more strongly negative in the 
    tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
    and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
    $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
    for vulnerability; Fig.~\ref{BIT}. The best-fit model for generality did not include any terms
    for latitude in any ecosystem type.

@@

\begin{figure}[h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the estimated scaling exponent for species richness (black
line) with its 95\% confidence interval (in grey),
based on N=196 empirical food webs. Latitude is 
given in degrees from the equator
regardless of direction.}
\label{S}
\end{figure}

>>>>

    Unlike species richness, only generality showed an overall increase with
    increasing proportions of basal resources in a web ($\beta_0$=0.019,
    $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
    link density, generality, and vulnerability, respectively;
    Fig.~\ref{TL_rescaled}). In each case, however, there were substantial
    effects of latitude on the scaling relationships. Thus, the scaling
    exponents for link density and vulnerability were negative for estuarine,
    lake, and stream communities and became more negative towards the poles
    ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
    $p$\textless0.001, respectively; Fig.~\ref{B}). For the scaling of link
    density and vulnerability in marine and terrestrial communities, the overall
    effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
    $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
    $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
    $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
    that there was weak scaling at most latitudes. In contrast, the scaling
    exponent of generality with the proportion of basal resources was positive
    near the equator and negative near the poles in estuarine, lake, and stream
    communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
    very little change in the scaling exponents for marine and terrestrial
    communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
    $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).

    As with species richness, link density, generality, and vulnerability
    generally increased with the proportion of intermediate consumers in a web
    ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
    $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{TL_rescaled}). 
    The best-fit models for link density and vulnerability did not include
    any effect of latitude. In contrast, the strength of the scaling relationship
    for generality increased weakly towards the poles in estuarine, marine, and
    terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
    towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
    and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{I}).

    In contrast to the generally positive scaling relationships above, link
    density, generality, and vulnerability decreased as the proportion of top
    predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
    $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
    Fig~\ref{TL_rescaled}). For estuarine, lake, and marine food webs the
    strength of this scaling did not vary significantly with latitude
    ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
    $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
    In stream and terrestrial food webs, however, scaling was more strongly negative in the 
    tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
    and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
    $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
    for vulnerability; Fig.~\ref{T}. The best-fit model for generality did not include any terms
    for latitude in any ecosystem type.

@@
